Understanding the impacts of video-guided activities on parent-child interaction

### 2020-04-08 paper/appendix-Bayesian-analyses.Rmd
fixed a couple NAs and line 328 issue, and improved appendix

get_stan_glmer_reporting_values <- function(model, cond, digits=3) {
  ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
  ci89 <- posterior_interval(model, prob = 0.89, pars = cond) # 89% CIs as recommended by Kruschke and others
  pd = p_direction(model)
  pd = pd[which(pd$Parameter==cond),]$pd
  ci = round(c(ci95,ci89,pd), digits)
  names(ci) = c("95pLB","95pUB","89pLB","89pUB","pd") # 95% and 89% lower and upper bounds
  beta = round(model$coefficients[cond], digits)
  return(c(beta,ci))
}
```

@@

e1ed = get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
pd = p_direction(types_modE, effects="fixed") # cond 82.5% EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%
```

@@

```{r, parent-ed-effect, echo=F, fig.cap="Figure 1. Posterior distribution of parent education coefficient with mean (red), 89% CIs (blue), and *pd* (orange portion) shown.", fig.width=4, fig.height=2.0}
dat = types_modE %>% posterior_samples("parent_ed") %>%
  estimate_density(extend=TRUE)

@@

```{r, plot-posteriors, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown."}
posterior <- as.matrix(types_modE)

#plot_title <- ggtitle("Posterior distributions", "with means and 89% credible intervals")
mcmc_areas(posterior,
           pars = c("conditionexp", 
                    "EL", "AA", "RR", 
                    "age", "genderM", "parent_ed", 
                    "conditionexp:EL",
                    "conditionexp:AA",
                    "conditionexp:RR"),
           prob = 0.89,
           prob_outer = 0.95,
           point_est = "mean") + #+ plot_title
  theme(plot.margin=unit(c(-30,2,2,2),"mm"))
```

>>>>

get_stan_glmer_reporting_values <- function(model, cond, digits=3) {
  ci95 <- posterior_interval(model, prob = 0.95, pars = cond)
  ci89 <- posterior_interval(model, prob = 0.89, pars = cond) # 89% CIs as recommended by Kruschke and others
  pd = p_direction(model)
  pd = pd[which(pd$Parameter==cond),]$pd
  ci = round(c(ci95,ci89,pd), digits)
  names(ci) = c("95pLB","95pUB","89pLB","89pUB","pd") # 95% and 89% lower and upper bounds
  beta = round(model$coefficients[cond], digits)
  return(c(beta,ci))
}

# pars are specific to E1
plot_posterior <- function(mod, title="") {
  posterior <- as.matrix(mod)
  plot_title <- ggtitle(title)
  mcmc_areas(posterior,
           pars = c("conditionexp", 
                    "EL", "AA", "RR", 
                    "age", "genderM", "parent_ed", 
                    "conditionexp:EL",
                    "conditionexp:AA",
                    "conditionexp:RR"),
           prob = 0.89, prob_outer = 0.95, point_est = "mean") + 
           theme(plot.margin=unit(c(-25,2,2,2),"mm")) +
           annotate("text", x = -0, y = 10.63, label = title)
}
```

@@

e1ed = get_stan_glmer_reporting_values(types_modE, 'parent_ed') 
pd = p_direction(types_modE, effects="fixed") # cond 82.5% EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%

tok_modE1 <- stan_glmer(paste("tokens", e1model_string), data=e1ld) 
mtld_modE1 <- stan_glmer(paste("MTLD", e1model_string), data=e1ld) 
ttr_modE1 <- stan_glmer(paste("TTR", e1model_string), data=e1ld) 
```

@@

```{r, parent-ed-effect, echo=F, fig.cap="Posterior distribution of parent education coefficient with mean (red), 89% CIs (blue), and *pd* (orange portion) shown.", fig.width=4, fig.height=2.0}
dat = types_modE %>% posterior_samples("parent_ed") %>%
  estimate_density(extend=TRUE)

@@

```{r, plot-posteriors, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown."}
plot_posterior(types_modE, title="Exp. 1: Word Types")
```

```{r, plot-token-posterior, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown."}

#e1ed = get_stan_glmer_reporting_values(tok_modE1, 'parent_ed') 
#pd = p_direction(tok_modE1, effects="fixed") # cond 82.5% EL 82.5% AA 87% genderM 93.2%, parent_ed 93.5% cond:AA 94.5%

plot_posterior(tok_modE1, "Exp. 1: Word Tokens")

```

```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting TTR, with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown.", warning=F}
plot_posterior(ttr_modE1, "Exp. 1: TTR")
```

```{r, echo=F, fig.width=6, fig.height=6, fig.cap="Posterior distributions for regression predicting MTLD, with means and 89% credible intervals. The outermost 5% of each posterior distribution is clipped and not shown."}
plot_posterior(mtld_modE1, "Exp. 1: MTLD")
```

### 2020-04-08 paper/manuscript.Rmd
fixed a couple NAs and line 328 issue, and improved appendix

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "5052"

@@

This theory of change is typically grounded in ideas about guided play and early language stimulation. 
Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens [@Malvern2004] or the context-appropriateness of the speech [@Cartmill2013], both of which have been linked to children's subsequent language development.
Further, language learning -- especially the acquisition of early vocabulary in the first years -- appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Baldwin1991; @Bigelow2004].
Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities [@Wood1976; @Weisberg2013].
Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play -- whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for rate (seconds per minute) of passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for rate (seconds per minute) of coordinated JA episodes.

@@

For each transcript of child-directed speech, the caregivers' unique word *types* and *tokens* (total words) uttered were tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity. 
Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010]. 
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (here we use the value proposed by @McCarthy2010: 0.720).

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution (i.e., probability of direction: *pd*; @Makowski2019), we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range (see Appendix for more an illustrated explanation).
There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`). 
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`]), with no notable influence of age.
Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: $\beta=`r e1types_condAA["conditionexp:AA"]`$, `r print_CI(e1types_condAA)`).
Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["RR"]`$, `r print_CI(e1pjaRR)`). 
However, higher RR parents who saw an Activity Video did not show this decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`). 
This regression also found that more educated parents showed a lower rate of passive JA episodes ($\beta=`r e1pja_parent_ed['parent_ed']`$, `r print_CI(e1pja_parent_ed)`).
Finally, parents made bids for JA at a higher rate with male children than with female children (male mean: `r round(e1bidsE_M[2,]$mean,2)` bids/min, female mean: `r round(e1bidsE_M[1,]$mean,2)`, $\beta=`r e1bidsE["genderM"]`$ `r print_CI(e1bidsE)`).

@@

### Participants. 
`r nrow(e2ld)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
(`r e2_12to18["Activity Video"]` 12-17.9 month-olds in the Activity Video condition; 
`r e2_12to18["Science Video"]` 12-17.9 month-olds in the Science Video condition; 
`r e2_18to24["Activity Video"]` 18-24 month-olds in the Activity Video condition;
`r e2_18to24["Science Video"]` 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1. 
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. 
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8). 
Sixteen parents reported their child was of Hispanic origin. 
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed[3]`), four-year college (n = `r e2_parent_ed[4]`), some graduate school (n = `r e2_parent_ed[5]`), to completed graduate school (n = `r e2_parent_ed[6]`) or declined to state (n = 13).

@@

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1. 
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44, 0.86] for total duration of passive JA episodes, and ICC = 0.88 with 95% CI = [0.75, 0.94] for total duration of coordinated JA episodes.

@@

[^6]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some of the below regressions led us to switch to Bayesian regression. Using a Bayesian analysis also has the added benefit of not requiring arbitrary decisions about changing alpha levels to attempt to correct for multiple comparisons (Gelman, 2008).

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , `r print_CI(e2TTR)`). 
The preregistered regression predicting the number of tokens used by parents revealed no effects. 
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table \ref{e2tab}.

```{r e2tab, echo=F}
e2 <- e2ld %>% group_by(Condition) %>%
  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
            "Mean types"=mean(types), types.sd=sd(types),
            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
names(e2) = c("Condition","TTR (M)", "(sd)", "MTLD (M)", "(sd)", "Types (M)", "(sd)", "Tokens (M)", "(sd)")
kable(e2, digits=2, caption="\\label{e2tab} Lexical diversity measures in Experiment 2.")
```

@@

We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, `r print_CI(e2bids)`)) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]). 
There were no other effects on parental bids for JA.

The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, e2tjaCond, with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, `r print_CI(e2tjaAge)`). 
However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, `r print_CI(e2tjaAgeCond)`): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, `r print_CI(e2cjaCond)`), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, `r print_CI(e2cjaAgeCond)`), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
The regression predicting the time spent in coordinated JA episodes found no notable effects.

Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, `r print_CI(e2pja)`), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, `r print_CI(e2pjat)`).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uhoh", "say", "for", "does", and "did".

@@

The short, activity-oriented parenting messages we used encouraged parents to make more attempts -- both verbal and non-verbal -- to engage their child, supporting their use as a component of interventions. 
Why were they successful? 
When parents are asked to play with their children in the presence of new toys, they may choose to follow their child's lead and engage in free play.
While free play is positive, it nevertheless results in less scaffolded activity than when parents are given a goal that suggests a repertoire of ways to guide their child. 
Parents may also persist in providing opportunities for their child to complete the activity, leading to more repetitive language but also more offers of engagement.

@@

This work was supported by a gift and a contract from Kinedu, Inc. to the Language and Cognition Lab. 
Thanks to members of the Language and Cognition Lab at Stanford for helpful discussion.

>>>>

abstract: |
  Early parenting practices play an important role in shaping the future  outcomes of young children [@Hart1995; @Heckman2006]. 
  In particular, high-quality early interactions and language input appear to  facilitate language learning and result in higher levels of school performance. 
  The rise of phone- and tablet-based parenting applications ("apps") holds the promise of delivering  low-cost, positive interventions on parenting style to a wide variety of populations. 
  Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions. 
  We showed parents a short video depicting an age-appropriate parent-child activity from a commercial parenting app, and found that the quality of parent-child interactions increases in some ways as a result of the intervention. 
  Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.
keywords          : "digital parenting advice; joint attention; lexical diversity; guided play"
wordcount         : "4995"

@@

This theory of change is typically grounded in ideas about guided play and early language stimulation. 
Child-directed speech varies not only in quantity (i.e., the number of total tokens), but also in quality in terms of the diversity of the tokens [@Malvern2004] or the context-appropriateness of the speech [@Cartmill2013], both of which have been linked to children's subsequent language development.
Further, language learning---especially the acquisition of early vocabulary in the first years---appears to be supported preferentially by parents and children _jointly attending_ to some object or activity [@Baldwin1991; @Bigelow2004].
Episodes of joint attention are frequent during guided play, when parents set goals and scaffold their child's activities [@Wood1976; @Weisberg2013].
Thus, the current literature supports interventions that encourage parents to provide high-quality language and interaction through something like guided play---whether via reading books or playing with a shape-sorter at home, or via a conversation about categories in the supermarket.

@@

A second coder independently coded a third of the videos (i.e., 20 of the 60 videos, approximately equally distributed across ages) to establish reliability. 
The two coders had a reliability of ICC = 0.79 with 95% confidence interval (CI) = [0.55, 0.91] for rate of parent bids for JA (number of bids per minute); ICC = 0.34 with 95% CI = [-0.11, 0.67] for rate of passive JA episodes (per minute); ICC = 0.66 with 95% CI = [0.32, 0.85] for rate of coordinated JA episodes; ICC = 0.33 with 95% CI = [-0.11, 0.67] for time spent (seconds per minute) in passive JA episodes, and ICC = 0.60 with 95% CI = [0.24, 0.82] for time spent in coordinated JA episodes.

@@

For each transcript of child-directed speech, the caregivers' unique word *types* and *tokens* (total words) uttered were tallied and converted to rates (e.g., tokens per minute of play), and the type-token ratio (TTR) was calculated as a measure of lexical diversity. 
Although we initially preregistered TTR as our measure of lexical diversity (since it is a simple, commonly used measure), it has been noted that TTR is correlated with the length of a text, which has led to the development of new measures such as the measure of textual lexical diversity [MTLD; @McCarthy2010]. 
Thus, we also measure lexical diversity with MTLD, which is calculated as the mean length of sequential word strings in a text that maintain a given TTR value (we use 0.72, as proposed by McCarthy & Jarvis).

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm [@rstanarm]. 
For effects that are at least 95% likely to be non-zero according to the posterior distribution (i.e., probability of direction: *pd*; @Makowski2019), we report estimated coefficients ($\beta$) as well as 89% Bayesian credible intervals (89% CI)[^4], demarcating the range within which 89% of the posterior falls, meaning that given the observed data, the effect has 89% probability of falling within this range (see Appendix for more an illustrated explanation).
There was lower TTR in the Activity Video condition (mean: `r round(subset(e1_lexdiv, condition=='exp')$TTR, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$TTR, 2)`, $\beta=$`r e1TTR["conditionexp"]`, `r print_CI(e1TTR)`). 
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: `r round(subset(e1_lexdiv, condition=='exp')$MTLD, 2)`) than in the No Video condition (mean: `r round(subset(e1_lexdiv, condition=='con')$MTLD, 2)`, $\beta=$`r e1MTLD["conditionexp"]`, `r print_CI(e1MTLD)`), with no notable influence of age.
Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR. 
These models included random intercepts per video. 
Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: $\beta=`r e1types_condAA["conditionexp:AA"]`$, `r print_CI(e1types_condAA)`).
Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes ($\beta=`r e1pjaRR["RR"]`$, `r print_CI(e1pjaRR)`). 
However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR:  $\beta=`r e1pjaE["ConditionActivity Video:RR"]`$, `r print_CI(e1pjaE)`). 
Parents with higher education also showed a lower rate of passive JA episodes ($\beta=`r e1pja_parent_ed['parent_ed']`$, `r print_CI(e1pja_parent_ed)`).
Finally, parents with male children made bids for JA at a higher rate (mean: `r round(e1bidsE_M[2,]$mean,2)` bids/min) than those with female children (mean: `r round(e1bidsE_M[1,]$mean,2)`, $\beta=`r e1bidsE["genderM"]`$, `r print_CI(e1bidsE)`).

@@

### Participants. 
`r nrow(e2ld)` infants (F = `r e2_gender['F']`, M = `r e2_gender['M']`) aged 12-24 months 
(`r e2_12to18["Activity Video"]` 12-17.9 month-olds in the Activity Video condition; 
`r e2_12to18["Science Video"]` 12-17.9 month-olds in the Science Video condition; 
`r e2_18to24["Activity Video"]` 18-24 month-olds in the Activity Video condition;
`r e2_18to24["Science Video"]` 18-24 month-olds in the Science Video condition) and their parents participated in the same museum as Experiment 1. 
We included infants who were exposed to English at least 75 percent of the time or who were exposed less but whose participating parent reported that they primarily speak English with their child at home. 
Forty-nine percent of participants (n = 41) had been exposed to two or more languages as indicated by their parent. 
Parents identified their children as White (n = 39), Asian (n = 20), African American/Black (n = 1), Biracial (n = 9), other (n = 7), or declined to state (n = 8). 
Sixteen parents reported their child was of Hispanic origin. 
Parents tended to be highly-educated, with reports of highest level of education ranging from some college (n = `r e2_parent_ed["3"]`), four-year college (n = `r e2_parent_ed["4"]`), some graduate school (n = `r e2_parent_ed["5"]`), to completed graduate school (n = `r e2_parent_ed["6"]`) or declined to state (n = 13).

@@

### Procedure. 
The procedure for Experiment 2 matched that of Experiment 1, except that parents in the Control Video condition watched a control video before the play session. 
Consistent with the No-Video control condition in Experiment 1, parents in the Control Video condition were told to play with their child as they would at home, and were not given additional instructions.
The coding procedure also matched that of Experiment 1. 
To establish reliability a second coder independently coded 25 of the 84 videos, approximately equally distributed across ages. 
The two coders had a reliability of ICC = 0.81 with 95% confidence interval (CI) = [0.62,0.91] for number of parent bids for JA; ICC = 0.74 with 95% CI = [0.48, 0.88] for number of passive JA episodes; ICC = 0.80 with 95% CI = [0.61, 0.91] for number of coordinated JA episodes; ICC = 0.72 with 95% CI = [0.44, 0.86] for time spent (secs/min) in passive JA episodes, and ICC = 0.88 with 95% CI = [0.75, 0.94] for time spent in coordinated JA episodes.

@@

[^6]: Although the preregistration implied the use of standard linear mixed-effects regression through the specification of adopting an alpha level of .005 for statistical significance, the non-convergence of some regressions led us to switch to Bayesian regression. Using a Bayesian analysis has the added benefit of not requiring arbitrary changes to alpha levels to correct for multiple comparisons (Gelman, 2008).

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: `r round(e2_lexdiv[2,]$TTR, 2)`) than after the Science Video (mean: `r round(e2_lexdiv[1,]$TTR, 2)`, $\beta=`r e2TTR["conditionexp"]`$, , `r print_CI(e2TTR)`). 
The preregistered regression predicting the number of tokens used by parents revealed no effects. 
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table 1.

```{r e2tab, echo=F}
e2 <- e2ld %>% group_by(Condition) %>%
  summarise("Mean TTR"=mean(TTR), TTRsd=sd(TTR),
            "Mean MTLD"=mean(MTLD), MTLDsd=sd(MTLD),
            "Mean types"=mean(types), types.sd=sd(types),
            "Mean tokens"= mean(tokens), tokens.sd=sd(tokens))
names(e2) = c("Condition","TTR", "(sd)", "MTLD", "(sd)", "Types", "(sd)", "Tokens", "(sd)")
#kable(e2, digits=2, caption="\\label{e2tab} Lexical diversity measures in Experiment 2.")
apa_table(e2, caption = "Mean lexical diversity measures in Experiment 2.")
```

@@

We fit Bayesian mixed-effects linear regressions predicting the rate of parental bids for joint attention and the rate of JA episodes as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Shown in Figure \ref{fig:JA} (left bottom), parents made bids for JA at a greater rate after watching the Activity Video (mean: `r round(subset(e2_bids, Condition=="Activity Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_bids, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Activity Video")$ci_upper,2)`]; $\beta=`r e2bids["ConditionActivity Video"]`$, `r print_CI(e2bids)`) than after the Science Video (mean: `r round(subset(e2_bids, Condition=="Science Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_bids, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_bids, Condition=="Science Video")$ci_upper,2)`]). 
There were no other effects on parental bids for JA.

The regression predicting rate of JA episodes revealed an effect of condition ($\beta=`r e2tjaCond["ConditionActivity Video"]`$, `r print_CI(e2tjaCond)`), with JA episodes occurring at a greater rate after the Activity Video (mean: `r round(subset(e2_tja, Condition=="Activity Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_tja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_tja, Condition=="Science Video")$mean,2)`, 95% conf. int.: [`r round(subset(e2_tja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_tja, Condition=="Science Video")$ci_upper,2)`]).
Older children also participated in JA episodes at a lesser rate than younger children ($\beta=`r e2tjaAge["age"]`$, `r print_CI(e2tjaAge)`). 
However, this age effect was moderated in the Activity Video condition ($\beta=`r e2tjaAgeCond["age:ConditionActivity Video"]`$, `r print_CI(e2tjaAgeCond)`): shown in Figure \ref{fig:JA} (right bottom), older children did not engage in episodes of JA at a lower rate after an activity video.

@@

Four additional exploratory regressions with a similar structure were carried out to predict the number and duration of coordinated and passive JA episodes.
The regression predicting the rate of coordinated JA episodes found an effect of condition ($\beta=`r e2cjaCond["ConditionActivity Video"]`$, `r print_CI(e2cjaCond)`), with a greater rate of coordinated JA episodes occurring after the Activity Video (mean: `r round(subset(e2_cja, Condition=="Activity Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Activity Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Activity Video")$ci_upper,2)`]) than after the Control Video (mean: `r round(subset(e2_cja, Condition=="Science Video")$mean,2)`, 95% CI: [`r round(subset(e2_cja, Condition=="Science Video")$ci_lower,2)`, `r round(subset(e2_cja, Condition=="Science Video")$ci_upper,2)`]).
There was an interaction of age and condition ($\beta=`r e2cjaAgeCond["age:ConditionActivity Video"]`$, `r print_CI(e2cjaAgeCond)`), shown in Figure \ref{fig:e2ja-coord}, revealing that after an Activity Video older children participated in coordinated JA episodes at a greater rate than children in the Control Video condition.
The regression predicting the time spent in coordinated JA episodes found no notable effects.
Older children both engaged in episodes of passive JA at a greater rate with their caregiver ($\beta=`r e2pja["age"]`$, `r print_CI(e2pja)`), and spent more time in passive JA with their caregiver ($\beta=`r e2pjat["age"]`$, `r print_CI(e2pjat)`).
Overall, these results show that the older children in our sample engage in more and longer episodes of joint attention with their caregivers, and that activity videos in particular lead to more episodes of coordinated JA.

As for Experiment 1, we conducted a corpus characteristic analysis to examine differences parents' language use in the two conditions.
The words that were strongly indicative of being from the Activity Video condition include "big", "little", "give", "small", "cow", "yellow", "take", and "put", while words that were most characteristic of the Science Video condition include "beep", "like", "neigh", "uh-oh", "say", "for", "does", and "did".

@@

The short, activity-oriented parenting messages we used encouraged parents to make more attempts---both verbal and non-verbal---to engage their child, supporting their use as a component of interventions. 
Why were they successful? 
When parents are asked to play with their children in the presence of new toys, they may choose to follow their child's lead and engage in free play.
While free play is positive, it nevertheless results in less scaffolded activity than when parents are given a goal that suggests a repertoire of ways to guide their child. 
Parents may also persist in providing opportunities for their child to complete the activity, leading to more repetitive language but also more offers of engagement.

@@

This work was supported by a gift and a contract from Kinedu, Inc. to the Language and Cognition Lab. 
Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion.
